### 2021-04-15 paper.Rmd
Link to github added to acknowledgements.
reshape figures

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus001.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus017.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus064.png}}
\centerline{
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus068.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus075.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus100.png}
}
\caption{Still views of a tour showing the space of possible two-dimensional projections as a torus shape in grey, and the trace of two short paths obtained via geodesic interpolation traced in color.}
\label{fig:interpolation-2d}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/notation-display-1d.pdf}
\includegraphics[width=0.3\textwidth]{figures/notation-display-2d.pdf}
\includegraphics[width=0.3\textwidth]{figures/notation-display-5d.pdf}
\caption{Various displays of the projections: 1D display in histogram (left), 2D display in scatterplot (middle), and 5d display in parallel coordinate plot (right).}
\label{fig:display}
\end{figure}

@@

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{figures/roman-surface-centered-010.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/torus-4-centered-015.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/cube-6-centered-001.png}}
\centerline{
\includegraphics[width=0.2\textwidth]{figures/roman-surface-centered-032.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/torus-4-centered-033.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/cube-6-centered-063.png}
}
\caption{Still views of the slice tour display showing geometric shapes: Roman surface (left), 4D torus (middle) and a 6d cube (right). (Adapted from Laa, Cook and Valencia, 2020, Figure 4.)}
\label{fig:tour-slice}
\end{figure*}

>>>>

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.3\textwidth]{figures/notation-torus-frames/torus001.png}
\includegraphics[width=0.3\textwidth]{figures/notation-torus-frames/torus017.png}
\includegraphics[width=0.3\textwidth]{figures/notation-torus-frames/torus064.png}}
\centerline{
\includegraphics[width=0.3\textwidth]{figures/notation-torus-frames/torus068.png}
\includegraphics[width=0.3\textwidth]{figures/notation-torus-frames/torus075.png}
\includegraphics[width=0.3\textwidth]{figures/notation-torus-frames/torus100.png}
}
\caption{Still views of a tour showing the space of possible two-dimensional projections as a torus shape in grey, and the trace of two short paths obtained via geodesic interpolation traced in color.}
\label{fig:interpolation-2d}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/notation-display-1d.pdf}
\includegraphics[width=0.3\textwidth]{figures/notation-display-2d.pdf}
\includegraphics[width=0.3\textwidth]{figures/notation-display-5d.pdf}
\caption{Various displays of the projections: 1D display in histogram (left), 2D display in scatterplot (middle), and 5D display in parallel coordinate plot (right).}
\label{fig:display}
\end{figure}

@@

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.3\textwidth]{figures/roman-surface-centered-010.png}
\includegraphics[width=0.3\textwidth]{figures/torus-4-centered-015.png}
\includegraphics[width=0.3\textwidth]{figures/cube-6-centered-001.png}}
\centerline{
\includegraphics[width=0.3\textwidth]{figures/roman-surface-centered-032.png}
\includegraphics[width=0.3\textwidth]{figures/torus-4-centered-033.png}
\includegraphics[width=0.3\textwidth]{figures/cube-6-centered-063.png}
}
\caption{Still views of the slice tour display showing geometric shapes: Roman surface (left), 4D torus (middle) and a 6d cube (right). (Adapted from Laa, Cook and Valencia, 2020, Figure 4.)}
\label{fig:tour-slice}
\end{figure*}
